Automated Reasoning of Relational properties using \\ Abstact Conflict Driven Clause Learning

### 2016-09-23 deductions.tex
deduction text updated

begin{figure}[t]
\tiny
\begin{tabular}{l|l}
\hline
Main Module & Interface Functions \\
\hline
\begin{lstlisting}
int main() {
 unsigned x, y;
 __CPROVER_assume(x==y);
 x++;
 assert(x==y+1);
}
\end{lstlisting}
&
\begin{lstlisting}[mathescape=true,language=C]
$cond#19 == (x#16 == y#18)
$guard#20 == ($cond#19 && $guard#0)
x#20 == 1u + x#16
x#20 == 1u + y#18 || !$guard#20
$guard#0 == TRUE
\end{lstlisting}
\\
\hline
\end{tabular}
\caption{C Program ad its corresponding SSA}
\label{sw-ssa}
\end{figure}

@@

\subsection{Chaotic Iteration Strategy}  
The set of octagonal equilities corresponding to Figurei~\ref{sw-ssa}
is shown below. For chaotic, no decision is required to deduce BOTTOM.
x#20 > 1                                                                      
-x20 - y18 < -2                                                               
-x16 - x20 < -2                                                               
y18 - x20 < 0                                                                 
x16 - x20 < 0                                                                 
y18 > 0                                                                       
x16 > 0                                                                       
-x20 - y18 < 0                                                                
x16 + y18 > 1                                                                 
y18 - x16 < 1                                                                 
x20 - y18 < 2                                                                 
x16 - y18 < 1                                                                 
cond19                                                                        
x16 + y18 > 0                                                                 
guard20                                                                       
guard0                                                                        
x16 + x20 > 0                                                                 
x20 - x16 < 2

@@

void main() {
 int x,y,z;
 _Bool c;
 if (c)
   x = -1;
 else
   x = 2;
 int k = id(x);
 z = x * k;
 assert((z!=-2));
}

>>>>

\begin{figure}[t]
\scriptsize
\begin{tabular}{l|l}
\hline
C program & SSA \\
\hline
\begin{lstlisting}[mathescape=true,language=C]
int main() {
 unsigned x, y;
 __CPROVER_assume(x==y);
 x++;
 assert(x==y+1);
}
\end{lstlisting}
&
\begin{lstlisting}[mathescape=true,language=C]
cond == (x == y)
guard1 == (cond19 && guard0)
x' == 1u + x
x' == 1u + y || !guard1
guard0 == TRUE
\end{lstlisting}
\\
\hline
\end{tabular}
\caption{C Program ad its corresponding SSA}
\label{sw-ssa}
\end{figure}

@@

\subsection{Chaotic Iteration Strategy}  
The set of octagonal equilities corresponding to Figurei~\ref{sw-ssa}
is shown below. For chaotic, no decision is required to deduce BOTTOM.
\begin{figure}[t]
\scriptsize
\begin{tabular}{l}
\hline
Octagonal Inequalities \\
\hline
\begin{lstlisting}
x' > 1                                                                      
-x' - y < -2                                                               
-x - x' < -2                                                               
y - x' < 0                                                                 
x - x' < 0                                                                 
y > 0                                                                       
x > 0                                                                       
-x' - y < 0                                                                
x + y > 1                                                                 
y - x < 1                                                                 
x' - y < 2                                                                 
x - y < 1                                                                 
x + y > 0                                                                 
x + x' > 0                                                                 
x' - x < 2  
\end{lstlisting}
\\
\hline
\end{tabular}
\caption{Octagonal Inequalities}
\label{sw-ssa}
\end{figure}

@@

void main() {
 int x,y,z;
 \_Bool c;
 if (c)
   x = -1;
 else
   x = 2;
 int k = id(x);
 z = x * k;
 assert((z!=-2));
}
